---
title: "gitflow notes"
author: "SG"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Source

All information taken from:
* <https://www.atlassian.com/git/tutorials/comparing-workflows/gitflow-workflow>

<https://stackoverflow.com/questions/3392392/when-is-the-right-time-to-delete-a-git-feature-branch>
<https://gist.github.com/JamesMGreene/cdd0ac49f90c987e45ac>

# Workflow

## Initiate

Create an empty develop branch locally and push it to the server:

```{r, engine = 'bash'}
git branch develop
git push -u origin develop
```

* Note: Other developers should now clone the central repository and create a 
tracking branch for develop.

## Create a feature branch

### Start

```{r, engine = 'bash'}
git checkout -b feature/MYFEATURE develop
```

### Finalize

Merge the feature_branch into develop.

```{r, engine = 'bash'}
git checkout develop
git merge --no-ff feature/MYFEATURE
git branch -d feature/MYFEATURE
```

## Creating a release

### Create a release branch

```{r, engine = 'bash'}
git checkout -b release/1.2.0 develop
```

### Release

Merge to master and develop, delete the release branch.

```{r, engine = 'bash'}
git checkout master
git merge --no-ff release/1.2.0
git tag -a 1.2.0
git checkout develop
git merge --no-ff release/1.2.0
git branch -d release/1.2.0
```

### Push to server

```{r, engine = 'bash'}
git push origin master
git push origin develop
git push origin --tags
git push origin :release/1.2.0 #if pushed
```


# Versioning advice

<http://r-pkgs.had.co.nz/description.html#version>

* A released version number consists of three numbers, <major>.<minor>.<patch>. 
For version number 1.9.2, 1 is the major number, 9 is the minor number, and 2 
is the patch number. Never use versions like 1.0, instead always spell out the 
three components, 1.0.0.

* An in-development package has a fourth component: the development version. 
This should start at 9000. For example, the first version of the package should
be 0.0.0.9000. There are two reasons for this recommendation: first, it makes 
it easy to see if a package is released or in-development, and the use of the 
fourth place means that you’re not limited to what the next version will be. 
0.0.1, 0.1.0 and 1.0.0 are all greater than 0.0.0.9000.

* Increment the development version, e.g. from 9000 to 9001 if you’ve added an 
important feature that another development package needs to depend on.

# Hotfix

```{r, engine='bash'}
git checkout master
git checkout -b hotfix/1.2.1 [commit]
```

```{r, engine='bash'}
git checkout master
git merge --no-ff hotfix/1.2.1
git tag -a 1.2.1
git checkout develop
git merge --no-ff hotfix/1.2.1
git branch -d hotfix/1.2.1
```

```{r, engine = 'bash'}
git push origin master
git push origin develop
git push origin --tags
git push origin :hotfix/1.2.1 # (if pushed)
```

