---
title: "Basic Git Workflows"
author: "SG"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Merge branch

```{r, engine = 'bash'}
# Change to branch that will receive merge
git checkout master
git merge development

# Optionally, merge from master to development first to check for conflicts
```

# Delete branch

```{r, engine = 'bash'}
# Locally
git branch -d branch_name
# Remotely
git push origin --delete {the_remote_branch}
```

To remove a local branch from your machine:

git branch -d {the_local_branch} (use -D instead to force deleting the branch without checking merged status)

To remove a remote branch from the server:



# Create new branch

```{r, engine = 'bash'}
git checkout -b [name_of_your_new_branch]
```

To add to remote

```{r, engine='bash'}
git push origin new_branch
```


# Undoing work

https://stackoverflow.com/questions/4114095/how-to-revert-git-repository-to-a-previous-commit
https://blog.github.com/2015-06-08-how-to-undo-almost-anything-with-git/

The following will create a new branch based on the specified commit identifier.

```{r, engine = 'bash'}
git checkout -b old-state 0d1d7fc32
```

Get rid of everything you've done since then

```{r, engine = 'bash'}
git reset --hard 0d1d7fc32
```

# Rename branch

Rename your local branch.

```{r, engine = 'bash'}

# If you are on the branch you want to rename:
git branch -m new-name

# If you are on a different branch:
git branch -m old-name new-name

```

**If you need to make changes to a remote branch as well:**

Delete the old-name remote branch and push the new-name local branch.

```{r, engine = 'bash'}
git push origin :old-name new-name
```

Reset the upstream branch for the new-name local branch

```{r, engine = 'bash'}
# Switch to the branch
git checkout new-name
git push origin -u new-name

```

# Add all to git

```{r, engine = 'bash'}
git add --all
git commit -am "<commit message>"
git push
```

# Unstage all

```{r, engine = 'bash'}
git reset
```

# Resolve conflict

```{r, engine='bash'}
# Fix changes
git add .
git commit -m "Resolved merge conflict by incorporating both suggestions."
```

# Add a tag

```
git tag -a tagname
```


# Removing tags

```{bash}
# use the --delete option for remote
git push --delete origin tagname

# If you also need to delete the local tag, use:
git tag --delete tagname

```

