---
title: "Workflow Cheatsheet: Package Development"
author: "SG"
output: github_document
---

# Start Project

* Start a new project
  * devtools::create("path/to/package/pkgname")
  * Or via "File" dropdown menu

# Develop Project

## Writing functions

* Add functions by creating .R files within "/R"
* Reload package using (ctrl-shift-L or devtools::load_all())

## External functions

* `devtools::use_package("name_of_package")` to add package to `import` field of
**DESCRIPTION** 
* Specify a version number manually in **DESCRIPTION**
* <http://r-pkgs.had.co.nz/description.html#dependencies>

### Using specific package functions

* Specify function as `package::function` in R code
* If implementing specific function numerous times, create a new file in "/R"
with comment: `#' @importFrom pgk fun`
* To utilize functions from entire package: `#' @import pgk`
* Include `NULL` on the last line following the comment.
* http://r-pkgs.had.co.nz/namespace.html

* If you want a package to be attatched when yours is attatched, add it to the 
`Depends` field of **DESCRIPTION**

# Documenting

## Generated via .R file using roxygen2

### Example

```{r}
#' Generate an htmlTable from tidy data
#'
#' A wrapper script for \code{htmlTable} that will build an htmlTable using
#' tidy data and mapping elements of the table to specific columns.
#'
#' All the details go here and they will be placed after the argument
#' descriptions.
#'
#' @param x The tidy data used to build the table
#' @param value The individual values which will fill each cell of the
#' table
#' @param header_td The column in \code{x} specifying column headings
#' @param rnames_td The column in \code{x} specifying row names
#' @param rgroup_td The column in \code{x} specifying row groups
#' @param hidden_rgroup rgroups that will be hidden.
#' @param cgroup1_td The column in \code{x} specifying the inner most column
#'  groups
#' @param cgroup2_td The column in \code{x} specifying the outer most column
#'  groups
#' @param tspanner_td The column in \code{x} specifying tspanner groups
#' @param hidden_tspanner tspanners that will be hidden.
#' @param debug_l Setting to true will print a message at certain points in the
#' execution of the function. This is meant to only be a temporary feature
#' as I learn to better utilizing existing debugging features in R Studio.
#' @param ... Additional arguments that will be passed to the inner
#' \code{htmlTable} function
#' @return Returns html code that will build a pretty table
#' @export
#' @seealso \code{\link[htmlTable]{htmlTable}}
#' @examples
#' \dontrun{
#' library(tidyverse)
#' mtcars %>%
#'     rownames_to_column %>%
#'     select(rowname, cyl, gear, hp, mpg, qsec) %>%
#'     gather(per_metric, value, hp, mpg, qsec) %>%
#'     group_by(cyl, gear, per_metric) %>%
#'     summarise(Mean = round(mean(value), 1),
#'               SD = round(sd(value), 1),
#'               Min = round(min(value), 1),
#'               Max = round(max(value), 1)) %>%
#'      gather(summary_stat, value, Mean, SD, Min, Max) %>%
#'      ungroup %>%
#'      mutate(gear = paste(gear, "Gears"),
#'             cyl = paste(cyl, "Cylinders")) %>%
#'      htmlTable_td(header_td = "gear",
#'                   cgroup1_td = "cyl",
#'                   cell_value = "value",
#'                   rnames_td = "summary_stat",
#'                   rgroup_td = "per_metric")
#' }
```

### Easily forgotten tags

```{r, eval = FALSE}
# Use parameters from other function
#' @inheritParams source_function

#' @describeIn source_function

# Reference other functions
## If in different package
#' @seealso \code{\link[package]{function}}
## If in same package
#' @seealso \code{\link{function}}

# To highlight as in-line code
#' \code{x}

# To add additional sections
#' @section SectionName:

# Adding a link
#' \code{\link{Summary}}

# If you have a family of related functions where every function should link to 
# every other function in the family
#' @family aggregate functions

# Ordered list
#' \enumerate{
#'   \item First item
#'   \item Second item
#' }

# Unordered list
#' \itemize{
#'   \item First item
#'   \item Second item
#' }

```

## Documenting Functions

* Build using
  * ctrl-shift-D
  * `devtools::document()`
* http://r-pkgs.had.co.nz/man.html#man-functions

## Documenting S3 generics and methods

* Document the generic as you would a function
* The methods don't necessarily need documentation

## Overall package documentation
* Generated using roxygen2 with stand-alone .R file in /R
* Include `NULL` after comments
* pg 51 of R Packages
* http://r-pkgs.had.co.nz/man.html#man-packages

# Edit the DESCRIPTION file

* Complete using inline instructions (generated automatically)

# Licensing

`devtools::use_gpl3_license`
`devtools::use_mit_license`
* Licensing is a bit complicated: https://choosealicense.com/

# Cleanup

## CRAN
* `running devtools::check()`

## Other packages
* `lintr` or `formatR` packages
* `lintr::lint_package()`
  * Adds markers to code and allow for manual cleanup

# Placing under Git control

* `devtools::use_git()`
* OR: tools->project options-> verison control
* Also, when starting a new package using the "File" dropdown menu, this can be 
automatically implemented
* Use the upper right Git panel to select files to stage and commit
* http://r-pkgs.had.co.nz/git.html

## Synchronizing with github
* create a new repository on github
* pull to local repository using the following bash commands:

```{bash, eval = FALSE}

git remote add origin git@github.com:graggsd/sgdemtbl.git
git push -u origin master

```

* http://r-pkgs.had.co.nz/git.html#github-init

## To update the remote repository

* commit files
* hit the push button

# Testing

* `devtools::use_testthat()`
* Create a .R file for each test in `projDir/tests/testthat/`
* Use described at the top by context("Use")

```{r, eval = FALSE}
context("complete")

test_that("basic invocation works", {
  df <- tibble(x = 1:2, y = 1:2, z = 3:4)
  out <- complete(df, x, y)
  expect_equal(nrow(out), 4)
  expect_equal(out$z, c(3, NA, NA, 4))
})
# From tidyr
# Other testing statements would follow

```


* Each test should evaluate specific functions and check a set of 
expectations
* See pg 74
* <http://r-pkgs.had.co.nz/tests.html>
* <https://github.com/tidyverse/tidyr/tree/master/tests>

# Continuous Integration

## Travis
* Flip switch on travis account
* `devtools::use_travis()`
* Add image to `README` file to display build status on github page.
* [![Build Status](https://travis-ci.org/tidyverse/dplyr.svg?branch=master)](https://travis-ci.org/tidyverse/dplyr)
* Make sure to knit to generated `.md` file (ctrl+shift+k)

## AppVeyor
* Go to AppVeyor site and click on New Project
* `devtools::use_appveyor()`
* Add badge to README (project settings and the badges tab)
* Ex: [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidyverse/dplyr?branch=master&svg=true)](https://ci.appveyor.com/project/tidyverse/dplyr)

# Using data

* http://r-pkgs.had.co.nz/data.html#data-extdata

## Exported data

* `devtools::use_data_raw()`
* place data into new directory
* write script to process data
* `devtools::use_data()`

## Give users access to raw data

* create inst/extdata and place data there
* Include documentation on how to access data via 
system.file("extdata", package = "packagename")

## For use in testing

* include small datasets directly in testing directory

## To run tests 

* `devtools::test()`
* ctrl + shift + T 

# Vignettes

* `devtools::use_vignette("my-vignette")`
* Modify `title`, `author` and `%\VignetteIndexEntry{Vignette Title}` fields
* `devtools::build_vignettes()` (to knit markdown file)
* OR Ctrl + Shift + K
* http://r-pkgs.had.co.nz/vignettes.html

# README

* devtools::use_readme_rmd()
* http://r-pkgs.had.co.nz/release.html#readme

# Renaming a package

<https://www.njtierney.com/post/2017/10/27/change-pkg-name/>

# Part 1: Changing the R package name

1. update your DESCRIPTION file package name
2. update the NEWS.md
3. update the name in the README file
4. update the .RProj name
5. update the folder name
6. update your package-.R file
7. Do a search (Cmd/Ctr + Shift + F) and look for mentions of your package name

# Part 2: Changing the github name

1. Now, with this final setp, what you want to do is go into your github repo, 
go to settings, then change the repo name.

2. You will then need to tell git where to look for your package online, 
as the URL has changed.

```{r, engine="bash"}
# First, let’s show where the origin is.
git remote show origin
# Then, remove the origin, with
git remote rm origin
# Nothing will happen. That is good. Now, check that you have no origin file.
git remote show origin
# Great. Now, add the new origin.
git remote add origin https://github.com/<USERNAME/ORGANISATION>/<YOUR-NEW-REPO-NAME>.git
# Nothing will happen. This is good.
# Now, check that the remote has been set.
git remote show origin
# Great, now make your changes, then add them, then do a commit.
git add .
git commit -m "updated package doco to be clearer about what the data is"
# And then push them.
git push
# This is fine.
# 
# Before we can push these changes onto github, we need to tell it where to push to.
# 
# Do this with
git push -u https://github.com/<USERNAME/ORGANISATION>/<YOUR-NEW-REPO-NAME>.git

############ Alt --------------------

# Changing the name of the Github.com repository is fortunately easy. 
# Go to the URL of your Github package, click Settings near the top-right, 
# change the name under "Repository name", and finally click Rename.
```

