---
title: "R Programming"
author: "Stephen Gragg"
date: "3/2/2020"
output: 
    html_document:
        code_folding: hide
        number_sections: true
        toc: true
        toc_float: true
            collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

# function as an argument

[Ex 1](https://stackoverflow.com/questions/46940944/how-create-an-r-function-that-take-a-fun-as-parameter)

```{r}
myOp2 <- function(x, y, FUN = identity) FUN(x + y)

myOp2(1, 2)
## [1] 3

myOp2(1, 3, sqrt)
## [1] 2
```

[Ex 2](https://stackoverflow.com/questions/11885207/get-all-parameters-as-list)

* `do.call()`
[Example](https://mathewanalytics.com/2018/07/05/r-programming-notes-1/)
[Example](https://www.stat.berkeley.edu/~s133/Docall.html)
* Basically allows us to iterate over a series of arguments called to one
function

* `match.call()`
* `match.fun()`

# `...`

* There are several ways to work with `...`

## Capture evaluated `...`  [[Ref](http://adv-r.had.co.nz/Functions.html#function-arguments)]

* `...` allows unmatched function arguments to be passed within the function
as needed.
* `...` in some applications, `...` is often easier to wrok with as a list 

```{r, eval=FALSE}
f <- function(...) {
  names(list(...))
}
f(a = 1, b = 2)
#> [1] "a" "b"
```

## Capture un-evaluated `...`

### Basic use of `substitute`  [[Ref](http://adv-r.had.co.nz/Computing-on-the-language.html#capturing-expressions)]

* When defining a new function, it is often helpful to allow input values
from the new function be passed on directly to other functions within
* However, when calling the function with a given input, by default, the input 
is evaluated before it can be passed on, thus returning an unexpected result
* Code can be captured prior to evaluation using the `substitute()` function.
* In this way, input code of an argument can be passed straight to another 
function within

```{r}
xyplot3 <- function(x, y, ...) {
  substitute(xyplot(x ~ y, ...))
}
xyplot3(mpg, disp, data = mtcars, col = "red", aspect = "xy")
#> xyplot(mpg ~ disp, data = mtcars, col = "red", aspect = "xy")
```


### Capture all unevaluated expressions in `...` [[Ref](http://adv-r.had.co.nz/Computing-on-the-language.html#capturing-dots)]

* As in other cases, sometimes it is helpful to capture arguments within `...`
as a list.
* The following example allows you to do so without evaluating those arguments

```{r}
dots <- function(...) {
  eval(substitute(alist(...)))
}
```

[Example](https://www.r-bloggers.com/a-new-r-trick-for-me-at-least/)

# Capture name of function

```{r}
as.character(substitute(base))
```

