---
title: "Workflow Cheatsheet: Releasing to Cran"
author: "SG"
output: github_document
---
# Run `R CMD check`

```{r}
devtools::check()
```

# Check reverse dependencies

(If releasing a new version of an existing package.)

```{r}
devtools::revdep_check()
```

# Update version number

Remove dev version suffix (e.g. `0.8.1.9000` -> `0.8.1`)

# Update README.md and NEWS.md

# Document continuous integration

* Push semi-final version to github and check build status on Travis and 
Appveyor

# Create submission comments

1. Create a file in the top level of directory called `cran-comments.md`
2. Add to .Rbuildignore
3. Example of how this may be populated:

```{txt}
## Test environments
* local OS X install, R 3.1.2
* ubuntu 12.04 (on travis-ci), R 3.1.2
* win-builder (devel and release)

## R CMD check results
There were no ERRORs or WARNINGs. 

There was 1 NOTE:

* checking dependencies in R code ... NOTE
  Namespace in Imports field not imported from: 'R6'

  R6 is a build-time dependency.

## Downstream dependencies
I have also run R CMD check on downstream dependencies of httr 
(https://github.com/wch/checkresults/blob/master/httr/r-release). 
All packages that I could install passed except:

* Ecoengine: this appears to be a failure related to config on 
  that machine. I couldn't reproduce it locally, and it doesn't 
  seem to be related to changes in httr (the same problem exists 
  with httr 0.4).
```

# Merge with master and push

```{bash}
git checkout master
git merge --no-ff develop
git push
```

# Release

```{r}
devtools::release()
```

# If rejected

* Make associated changes
* Updated cran notes with comment at top

```{txt}
## Resubmission
This is a resubmission. In this version I have:

* Converted the DESCRIPTION title to title case.

* More clearly identified the copyright holders in the DESCRIPTION
  and LICENSE files.
```

* Run `devtools::check()`
* Resubmit with `devtools::submit_cran()`

# Prepare next version number

Tag master version with release. Then, switch to development version

```{bash}
# Tag the master version with the release
git tag -a v1.2.3
# Switch to development version
git checkout develop
merge master
```

Update version and append `.9000` to the end

# Publicise package

